Data Analysis

### 2022-06-17 03.data_analysis.Rmd
updating list

```{r}
library(dplyr)
library(bib2df)
library(rio)
library(tidyr)
library(ggplot2)
library(nlme)
library(RColorBrewer)
library(countrycode)
library(maps)
library(MOTE)
current_year <- 2022

## fixes
## update sau chins paper with new list https://osf.io/gq92w/ 
## make list of OSC
## add Many Primates list 
## update Dorison et al.

## double check each publication for proper year and journal
## look at merged id and incorrect ids 
```

@@

```{r}
bibs <- bib2df("papers.bib")

@@

In this section, we will add the information for authors when they used a consortium authorship.

```{r}

@@

- test the merge

@@

journal_count$JOURNAL[is.na(journal_count$JOURNAL)] <- "Pre-Print"
```

>>>>

```{r}
library(dplyr)
library(bib2df)
library(rio)
library(tidyr)
library(ggplot2)
library(nlme)
library(RColorBrewer)
library(countrycode)
library(maps)
library(MOTE)
current_year <- 2022
```

@@

```{r}
# bibs <- bib2df("papers.bib") original data
bibs <- bib2df("papers_06_17_22.bib")

@@

Note that we edited the references in Zotero directly to fill in corstium authorships.

@@

- test the merge to make sure we have all authors included

@@

journal_count$JOURNAL[is.na(journal_count$JOURNAL)] <- "Pre-Print"

# also add information about the preprint RR acceptances 
```
